\hypertarget{_development_tools_DevelopmentToolsCppIDEsforMacOSX}{}\section{C++ I\+D\+Es for Mac O\+S X}\label{_development_tools_DevelopmentToolsCppIDEsforMacOSX}
\hypertarget{_development_tools_DevelopmentToolsCppIDEsforMacOSXXcode}{}\subsection{Xcode}\label{_development_tools_DevelopmentToolsCppIDEsforMacOSXXcode}
Xcode is the default software development I\+D\+E for Mac os X. It provides everything developers need to create great applications for Apple computers (Mac, i\+Phone, and i\+Pad). Xcode has a good interface design, a good start up speed, and a good tool set for debugging. \hypertarget{_development_tools_DevelopmentToolsCppIDEsforMacOSXNetBeans}{}\subsection{Net\+Beans}\label{_development_tools_DevelopmentToolsCppIDEsforMacOSXNetBeans}
Net\+Beans I\+D\+E is originally built for Java development. It has a good scalability that provides plugins for C++ development. It is free and open source and has a large community of users and developers around the world. Net\+Beans is written in Java so that it may be slower compared to native binary applications. \hypertarget{_development_tools_DevelopmentToolsCppIDEsforMacOSXEclipse}{}\subsection{Eclipse}\label{_development_tools_DevelopmentToolsCppIDEsforMacOSXEclipse}
Eclipses is similar to Net\+Beans. The only difference may be it has more plugins and slower.\hypertarget{_development_tools_DevelopmentToolsDocumentation}{}\section{Documentation}\label{_development_tools_DevelopmentToolsDocumentation}
\hypertarget{_development_tools_DevelopmentToolsDocumentationDoxygen}{}\subsection{Doxygen}\label{_development_tools_DevelopmentToolsDocumentationDoxygen}
Doxygen is the documentation tool for generating A\+P\+I documentation from source code.\+It is developed under Mac os and Linux, but also it supports Window or other Unix-\/like operating systems. Doxygen supports languages like C++, C\#, Java, python, and etc. \hypertarget{_development_tools_DevelopmentToolsDocumentationGraphviz}{}\subsection{Graphviz}\label{_development_tools_DevelopmentToolsDocumentationGraphviz}
Graphviz is an open source graph visualization tool. It is easy to represent structural information as diagrams of abstract graphs and networks. Combining Doxygen and Graphviz can easily create O\+O\+P based U\+M\+L diagram. \hypertarget{_development_tools_DevelopmentToolsDocumentationUMLet}{}\subsection{Development\+Tools\+Documentation\+U\+M\+Let}\label{_development_tools_DevelopmentToolsDocumentationUMLet}
U\+M\+Let is a n open source U\+M\+L tool with a simple user interface. By using U\+M\+Let you can draw U\+M\+L diagrams very fast. It allows you build sequence and activity diagrams from plain text. U\+M\+Let runs stand-\/alone or as Eclipse plug-\/in on Windows, Mac O\+S X and Linux. 