Games development is one of the most exciting areas of software development that you can work in. Game developers require skills and expertise in modeling, graphics programming, game design, simulation and animation.\hypertarget{_game_development_GameDevelopmentGraphicsAPIs}{}\section{Graphics A\+P\+Is}\label{_game_development_GameDevelopmentGraphicsAPIs}
\hypertarget{_game_development_GameDevelopmentGraphicsAPIsOpenGL}{}\subsection{Open\+G\+L}\label{_game_development_GameDevelopmentGraphicsAPIsOpenGL}
Open\+G\+L is a multi-\/platform A\+P\+I for developing 2\+D and 3\+D graphics applications. Most of Libraries is based on Open\+G\+L, such as S\+F\+M\+L. Open\+G\+L is the industry\textquotesingle{}s most widely used and supported 2\+D and 3\+D graphics application programming interface, bringing thousands of applications to a wide variety of computer platforms. \mbox{[}\hyperlink{_reference_r1}{1}\mbox{]} \hypertarget{_game_development_GameDevelopmentGraphicsAPIsMicrosoftDirectX}{}\subsection{Microsoft Direct\+X}\label{_game_development_GameDevelopmentGraphicsAPIsMicrosoftDirectX}
Microsoft Direct\+X is a collection of A\+P\+Is designed to allow development of games and multimedia applications on Microsoft platforms. It is the graphics technology powering today’s most impressive games.\hypertarget{_game_development_GameDevelopmentMultimediaLibraries}{}\section{Multimedia Libraries}\label{_game_development_GameDevelopmentMultimediaLibraries}
\hypertarget{_game_development_GameDevelopmentMultimediaLibrariesSFML}{}\subsection{S\+F\+M\+L}\label{_game_development_GameDevelopmentMultimediaLibrariesSFML}
S\+F\+M\+L (Simple and Fast Multimedia Library) is a portable A\+P\+I written in C++ for multimedia programming based on Open\+G\+L and Open\+A\+L. It supports multiple programming languages such as C++ , Python, .Net and etc. It can be thought of as an object oriented alternative to S\+D\+L. S\+F\+M\+L provides hardware accelerated 2\+D graphics, and supports Open\+G\+L windowing and provides different modules that ease multimedia and game programming. \mbox{[}\hyperlink{_reference_r2}{2}\mbox{]} \hypertarget{_game_development_GameDevelopmentMultimediaLibrariesSDL}{}\subsection{S\+D\+L}\label{_game_development_GameDevelopmentMultimediaLibrariesSDL}
S\+D\+L (Simple Direct\+Media Layer) is a cross-\/platform development library designed to provide low level access to hardware via Open\+G\+L and Direct3\+D. It support multiple programming languages (C/\+C++, python, .Net and etc.) \mbox{[}\hyperlink{_reference_r3}{3}\mbox{]} 