The document describes all functionalities estimated to be implemented for the project. It also shows what level of quality of the project should be achieved. Project plan and schedule are embedded in this document. \hypertarget{_introduction_IntroductionPurpose}{}\section{Purpose}\label{_introduction_IntroductionPurpose}
The main purpose of my project is to create a C++ framework for parallel computing. Parallel computing is the science and art of programming computers that can do more than one operation at once during the same cycle, simultaneously and concurrently. It performs often via having more than one processor. ~\newline
~\newline
Next, A benchmark program is required for profiling this framework. The program will be designed as a G\+U\+I application which shows the performance in different situations \hypertarget{_introduction_IntroductionPlan}{}\section{Plan}\label{_introduction_IntroductionPlan}
Dual State Framework will be developed by C++ under Mac Os X. Open\+M\+P or Intel T\+B\+B is used for implementing Parallel Computing. In addition, it will be compiled and debugged both on Microsoft Windows and Linux as well. This process will be done by Cmake. The A\+P\+I Documentation of this project will be created by Doxygen. ~\newline
~\newline
The simple benchmark program will be written by C++ with S\+F\+M\+L or S\+D\+L library. Git will be used for source control and version control. The project is now available in following link. ~\newline
~\newline
\href{https://github.com/kuyoonjo/DualStateFramework}{\tt https\+://github.\+com/kuyoonjo/\+Dual\+State\+Framework} \hypertarget{_introduction_IntroductionPotentialUsers}{}\section{Potential Users}\label{_introduction_IntroductionPotentialUsers}
Dual State Framework can have a variety of uses. Initially the project is concerned around computer games, but it can be used in broad kinds of software. The framework can be used in any program or game that runs parallel processes. Currently almost all of them meet that criteria. 